---
title: "DSRT Notebook"
output: html_notebook
---

R Notebook for displaying the DSRT Screen data and relevant analysis. 
Set the working directory:
```{r}
setwd("DSRT_Screen_Code")
```


Import the neccesary functions:
```{r}
source("Utilities/Utility_package.R")
source("Scripts/Drug_Synergy_Package.R")
```


Import the data:

```{r}
growth_effect_matrix = import_plate_range("Sample_Data/Sample_Excel_Template.xlsx", "N10:X16")
```


Print Heatmap Scaled:
```{r}
print_heatmap_bliss_scaled(growth_effect_matrix, export_name = "Sample_Output/Sample_Output_Scaled_Heatmap.jpg", xlabel = "Drug A", ylabel = "Drug B")
```

Print Heatmap Outlier:
```{r}
print_heatmap_bliss_outlier_elim(growth_effect_matrix, export_name = "Sample_Output/Sample_Output_Outlier_Heatmap.jpg", xlabel = "Drug A", ylabel = "Drug B")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
