---
title: "DSRT Notebook"
output: html_notebook
---

# R Notebook for Analyzing Synergy
R Notebook for displaying the DSRT Screen data and relevant analysis. 


## Setup Environment
Import the neccesary functions:
```{r}
source("Utilities/Utility_package.R")
source("Scripts/Drug_Synergy_Package.R")
source("Scripts/Drug_Logistic_Package.R")
```


## Import Data

```{r}
growth_effect_matrix = import_plate_range("Sample_Data/Sample_Excel_Template.xlsx", "N10:X16")
print(growth_effect_matrix)
```


## Basic Heatmap Functions

Print Heatmap Scaled:
```{r}
print_heatmap_bliss_scaled(growth_effect_matrix, export_name = "Sample_Outputs/Sample_Output/Sample_Output_Scaled_Heatmap.jpg", xlabel = "Drug A", ylabel = "Drug B")
```

Print Heatmap Outlier:
```{r}
print_heatmap_bliss_outlier_elim(growth_effect_matrix, 
                                 export_name = "Sample_Outputs/Sample_Output/Sample_Output_Outlier_Heatmap.jpg",
                                 xlabel = "Drug A", ylabel = "Drug B")
```

## Basic Pipeline Functionality

Here we will show how to Analyze all the XLSX files in a single folder using the Pipeline utility.
This version analyzes the files sequentially on one CPU

```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Pipeline_Output",sep = ""))
pipeline(pipelined_print_heatmap_growth_scaled,
         input_directory, 
         output_directory,
         additional_args = c("N10:X16"),
         parallel_run = FALSE,
         environment = lsf.str()) 
```

This version runs the same analysis, but in parallel on all available CPU cores. Analyzes one sheet per core. 
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Pipeline_Output",sep = ""))
pipeline(pipelined_print_heatmap_growth_scaled,
         input_directory, 
         output_directory,
         additional_args = c("N10:X16"),
         parallel_run = TRUE,
         environment = lsf.str()) 
```

## Basic Bliss Sum

Calculate a bliss sum in a couple of different ways:
```{r}
bliss_sum_scaled = calculate_bliss_sum_scaled(growth_effect_matrix)
bliss_sum_outlier = calculate_bliss_sum_outlier_elim(growth_effect_matrix)
print(bliss_sum_scaled)
print(bliss_sum_outlier)
```

## Bliss Sum Pipeline

Produce a .csv file with bliss sums for all items inside of a folder. Note, must be done sequentially since all sums point to the same file.
Very fast to produce however. 
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Bliss_Sum",sep = ""))
pipeline(pipelined_print_bliss_sum_growth_scaled,
         input_directory, 
         output_directory,
         additional_args = c("N10:X16","Bliss_Sum_Scaled.csv"),
         parallel_run = FALSE,
         environment = lsf.str()) 
```

## Recursive Pipeline 

Run Analysis on all files of a certain type within a directory. Note that the directory is created dynamically if it doesn't exit. 
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Recursive_Output",sep = ""))
pipeline_folder_recursive(pipelined_print_heatmap_growth_scaled,
                          input_directory,
                          output_directory,
                          additional_args = c("N10:X16"),
                          file_type = "xlsx",
                          parallel_run = TRUE,
                          cores = 8,
                          environment = lsf.str())
```

Note, if you would like to put the sample data next to the output, just use the same input and output directory. This is given below:
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = input_directory
pipeline_folder_recursive(pipelined_print_heatmap_growth_scaled,
                          input_directory,
                          output_directory,
                          additional_args = c("N10:X16"),
                          file_type = "xlsx",
                          parallel_run = TRUE,
                          cores = 8,
                          environment = lsf.str())
```

Run all analysis and place the files into a main folder that contains all the nested files.
Can run in parallel or sequentially. Note only the analysis in individual folders is run in parallel
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Recursive_Combined",sep = ""))
pipeline_folder_combine(pipelined_print_heatmap_growth_outlier_elim,
                          input_directory,
                          output_directory,
                          additional_args = c("N10:X16"),
                          file_type = "xlsx",
                          parallel_run = TRUE,
                          cores = 8,
                          environment = lsf.str())
```


# Synergy Functions using BioC

Thanks Clint for making this part!

## Import the Data as a Synergy Data Frame

input_file should be an xlsx file and the range defines where the growth data is at.
```{r}
input_file = "Sample_Data/Sample_Excel_Template.xlsx"
data_frames <- build_data_frame(input_file, range="N10:X16", Viability_Data = TRUE, 
                                Normalize = TRUE, Drug_A = "Docetaxel", Drug_B = "Luminespib",
                                Cell_Line = "Mia-PaCa-2", Conc_A = "uM", Conc_B = "uM", replicate = 1)
```

## Print Logistic Curves and Inflection Points

Note if Filename is left NULL it uses the name built into the data_frame above.
```{r}
print_logistic_function(data_frames, 
                        Logistic_Output_Folder = "Sample_Outputs/Sample_Logistic_Curves",
                        num_param_logistic = "all", filename = NULL)

```

Note if Filename is left NULL it uses the name built into the data_frame above.
```{r}
print_logistic_inflection_points(data_frames, 
                                 Inflection_Output_Folder = "Sample_Outputs/Sample_Inflection_Points",
                                 num_param_logistic = "all", filename = NULL)
```


## Print a Synergy Map

synergy_type can be: "HSA", "Loewe", "Bliss", or "ZIP" synergy method *ZIP combines the assumptions of both Loewe and Bliss models*
```{r}
synergy_analysis(data_frames, synergy_type = "Bliss", Output_Folder = "Sample_Outputs/Sample_Synergy",
                           filename = NULL)
```

## Pipeline Synergy Functions

Logistic Pipeline:
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Logistic_Combine",sep = ""))
pipeline_folder_combine(pipelined_Logistic_Curves,
                          input_directory,
                          output_directory,
                          additional_args = c("N10:X16", TRUE, TRUE, "all"),
                          file_type = "xlsx",
                          parallel_run = TRUE,
                          cores = 8,
                          environment = lsf.str())
```

Inflection Pipeline:
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Inflection_Combine",sep = ""))
pipeline_folder_combine(pipelined_Inflection_Curves,
                          input_directory,
                          output_directory,
                          additional_args = c("N10:X16", TRUE, TRUE, "all"),
                          file_type = "xlsx",
                          parallel_run = TRUE,
                          cores = 8,
                          environment = lsf.str())
```

Graph Pipeline:
```{r}
input_directory = toString(paste(getwd(),"/Sample_Data",sep = ""))
output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Synergy_Combine",sep = ""))
pipeline_folder_combine(pipelined_Synergy_Graphs,
                          input_directory,
                          output_directory,
                          additional_args = c("N10:X16", "Bliss", TRUE, TRUE),
                          file_type = "xlsx",
                          parallel_run = FALSE,
                          cores = 8,
                          environment = lsf.str())
```


## Combine Synergy Files

Here we combine the files in the synergy folder into one dataframe.
Works specifically for a directory full of CSV files that were produced in the above. 

```{r}
Input_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Synergy_Combine",sep = ""))
combined_frame = Combine_Synergy_Files(Input_directory)
```

Here we can combine the files and reprint a CSV of the combined files. 
if remove_csv is true, then destroy the file after reading it. 
```{r}
Input_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Synergy_Combine",sep = ""))
Output_directory = toString(paste(getwd(),"/Sample_Outputs/Sample_Synergy_Combine/Combined_Synergy",sep = ""))
Combine_Synergy_Files_CSV(Input_directory,
                          Output_directory,
                          Output_Filename = "Combined_Synergy",
                          allow_overwrite = FALSE,
                          remove_csv = TRUE)
```

